Synthesizing Quotient Lenses

### 2017-10-20 papers/QuotientLensSynth/main.tex
Made changes to the intro

However, these constraints are sometimes too strict. For example, a record in
the data may represented in many ways because of the presence of spurious
whitespace characters or because of the reordering of fields. Deriving a lens
which obeys the lens laws in such a case can be daunting and frustrating.

As a solution to this problem, Foster et al proposed {\em quotient lenses},
which are a generalization of lenses in which the source and target data are
considered modulo an equivalence relation. Quotient lenses are
both simpler and more flexible, since whole equivalence classes of data
values can be handled all at once and inessential details like whitespace
and ordering of fields can be ignored.

However many complicated equivalence relations are difficult to express in
Boomerang, the lens programming language in which Foster et al implemented
quotient lenses. For example, suppose that the \bibtex{} to EndNote
transformation is required to allow for whitespace to occur arbitrarily between
the words in the label, author and title fields as well as in between them, and
ignore the order in which the author and title fields occur in each record.
These rules allow for the \bibtex{} citations
\begin{verbatim}
    @Book {conway,
      Author = "J. H. Conway",
      Title = {Regular Algebra and Finite Machines},
    }
\end{verbatim}
and
\begin{verbatim}
    @Book{     conway,
        Title = {Regular Algebra 
                 and Finite Machines},
           Author = "J. H. Conway",     }
\end{verbatim}
to be considered the same, with the EndNote records having similar rules
defined on them.

While it is possible to express the equivalence on the \bibtex{} data above in
Boomerang, actually doing so is difficult. The difficulty arises from the fact
that the entire equivalence is composed of three separate equivalences which
nest and interact with each other in a way that makes them difficult to express
with the standard Boomerang combinators. Moreover, many of the equivalences
expressible in Boomerang require that the programmer first specify the data
itself in form of a regular expression before specifying the equivalence
relation on the data.

>>>>

However, the constraints imposed by the lens laws are often too strict. For
example, when a record may be represented in many ways, perhaps because
whitespace characters are allowed to occur arbitrarily in certain parts of the
data, deriving a lens which obeys the lens laws in such cases can be daunting
and frustrating.

As a solution to this problem, Foster et al proposed {\em quotient lenses},
which are a generalization of lenses in which the source and target data are
considered modulo an equivalence relation. Quotient lenses, which are
implemented as a refinement of the bidirectional string processing language
Boomerang, are both simpler and more flexible, since whole equivalence classes
of data values can be handled all at once and inessential details like
whitespace and ordering of fields can be ignored.

However many complicated equivalence relations are difficult to express in
Boomerang. For example, suppose that the \bibtex{} to EndNote
transformation which we introduced is required to allow for whitespace to occur
arbitrarily between the words in the label, author and title fields as well as
in between them, and ignore the order in which the author and title fields
occur in each record.
These rules allow for the \bibtex{} citations
\begin{verbatim}
    @Book {conway,
      Author = "J. H. Conway",
      Title = {Regular Algebra and Finite Machines},
    }
\end{verbatim}
and
\begin{verbatim}
    @Book{     conway,
        Title = {Regular Algebra 
                 and Finite Machines},
           Author = "J. H. Conway",     }
\end{verbatim}
to be considered the same, with the EndNote records having similar rules
defined on them.

While it is possible to express the equivalence on the \bibtex{} data above in
Boomerang, actually doing so is difficult. The difficulty arises from the fact
that the entire equivalence is composed of three separate equivalences which
nest and interact with each other in a way that makes them difficult to express
with the standard Boomerang combinators. Moreover, many of the equivalences
expressible in Boomerang, such as Boomerang's permutation combinator, require
that the programmer first specify the data itself in form of a regular
expression before specifying the equivalence relation on the data. This leads to
verbose code that is difficult to understand.
